\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-07-28 write_up/mixfishsim_ecolmod.tex
Revisions

To answer these questions we i) develop a simulation model where population
dynamics are highly-resolved in space and time\replaced[id=PD]{. Being}{ and
	are} known \added[id=PD]{directly} rather than inferred from sampling
or commercial catch\added[id=PD]{, we can use the population model to validate
	how inference from fisheries-dependent and fisheries independent
	sampling relates to the real community structure in a way we could not
	with real data}. We ii) compare, at different spatial and temporal
aggregations, the 'real population' distributions to samples from
fisheries-dependent and fisheries independent catches to test if these are a
true reflection of the relative density of the populations. We then iii)
simulate a fishery closure to protect a species based on different spatial and
temporal data aggregations. We use these evaluations to draw inference on the
utility of commercial data in supporting management decisions.
\todo{\added[id=JJ]{If the paper has two goals this should be clear from the
		start, but may be better over 2 MSs}\added[id=PD]{I would like
		to keep both parts, but have made clearer in how its set out.
		The closure scenarios form validation of the data aggregation,
		rather than effectiveness of the closures themselves - so its a
		continuation of the same question in my eyes}}\deleted[id=PD]{.
	Further, we extend our analysis to a range of spatial and temporal
	scales to assess the impact of these processes on the success of the
	management measure.}\\

@@

\deleted[id=PD]{The fishing model operated on a tow-by-tow basis, while}
\replaced[id=PD]{P}{p}opulation dynamics (fishing and natural mortality,
growth) operate on a daily time-step\replaced[id=PD]{, while p}{. P}opulation
movement occurs on a weekly time-step\replaced[id=PD]{. R}{, while r}ecruitment
\replaced[id=PD]{takes place}{occurs} periodically each year for a set time
\replaced[id=PD]{duration}{period (e.g. 3 weeks)} specified for each
population\deleted[id=PD]{.}\added[id=PD]{, while the fishing module operates
	on a tow-by-tow basis (i.e. multiple events a day)}.  
\deleted[id=PD]{Here we describe each of the model components; 1) Population
	dynamics, 2) Recruitment dynamics, 3) Population movement dynamics, 4)
	fishery dynamics.}

\replaced[id=PD]{In the model system p}{P}opulation movement is driven by
random (diffusive) and directed (advective) processes and we incorporate
characterisation of a number of different fishing \added[id=PD]{fleet dynamics}
exploiting four fish populations with different spatial and population
demographics. The following describes the implementation of each of the
sub-modules.

@@

The basic population level processes were simulated using a modified two-stage
Deriso-Schnute delay difference model \citep{Deriso1980, Schnute1985,
	Dichmont2003} occurring at a daily time-step. \added[id=PD]{A daily
	time-step was chosen to discretise continuous population processes on a
	biologically relevant and computationally tractable timescale.}
\deleted[id=PD]{Here,}Population
biomass growth and depletion for pre-recruits and\deleted[id=PD]{fish}
recruited \added[id=PD]{fish}\deleted[id=PD]{to the fishery} were modelled
separately as a function of previous recruited biomass, intrinsic population
growth and recruitment functionally linked to the adult population size.
Biomass for each cell $c$ was incremented each day $d$ as follows (the full
parameter list is detailed in Table \ref{tab: pop_variable}): 
\begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& (1 + \rho) B_{c,d} \cdot e^{-Z_{c,d}} - \rho \cdot e^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& (B_{c,d-1} \cdot e^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
	R_{\tilde{y}(c,y,d-1)})
	\hspace{0.4cm} + \\
	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(c,y,d)} 
	\end{split}
\end{equation}
where $\rho$ is Brody's coefficient, shown to be equal to $e^{-K}$ when $K$ is
the growth rate from a von Bertalanffy logistic growth model
\citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
represents the proportion of fish recruited during that day for the year, while
$R_{c,\tilde{y}}$ is the annual recruits in cell $c$ for year $y$. \\

@@

A fisheries-independent survey is simulated where fishing on a regular grid
begins each year at the same time for a given number of stations (a fixed
station survey design). Catches of the populations \replaced[id=JJ]{at each
station}{present} are recorded but not removed from the population. This
provides a fishery independent snapshot of the populations at a regular spatial
\replaced[id=JJ]{intervals}{distribution} each year, similar to scientific
surveys undertaken by fisheries research agencies. \\

@@

The following steps are undertaken to determine closures:
\todo{\added[id=JJ]{Procedure unclear. Refer to symbols in methods section or
		switch order starting with description of data type
		etc..}\added[id=PD]{Yes, will redo}}
\begin{enumerate}
	\item Extract data source
	\item Aggregate according to desired spatial and temporal resolution
	\item Interpolate across entire area at desired resolution using simple
		kriging using the \emph{interp} function from the R package
		akima \citep{Akima2006}. JM: SEE COMMENT
	\item Close area covering top 5 \% of catch rates 
\end{enumerate}
In total 28 closure scenarios were run that represent combinations of:

@@

Vessels from the same fleet (and therefore targeting preference) exploit
similar but slightly different fishing grounds depending on their own personal
experience during the explore phase of the fishery (\added[id=PD]{Figure}
\ref{S-fig:14}), that is the result of the randomness in the correlated random
walk step function, with distance moved during the exploitation phase and the
direction stochastically related to the revenue experienced on the fishing
ground (\replaced[id=PD]{Figure}{while}
\ref{S-fig:15}).\todo{\added[id=JJ]{Move some of the supplementary figures to
		the manuscript}}

@@

Figure \ref{fig:2} shows the consequences of different temporal aggregations of
the data over a ten-year period, with weekly (top), monthly (middle) and yearly
(bottom) catch compositions from across an aggregated 20 x 20 area. By
comparison to the 'real population', the monthly aggregation captures the major
patterns seen in the weekly data, albeit missing more subtle differences. The
yearly data results in a constant catch pattern due to the aggregation process
(sometimes known as an aggregation bias). The commercial data on a weekly basis
shows some of the same patterns as the 'real population', though the first
species (in red) is less well represented and some weeks are missing catches
from the area. The monthly data shows some consistency between the 'real
population' and commercial data for species 2 - 4, though species 1 remains
under-represented. On an annual basis, interestingly the commercial data under
represents the first species (in red) while the survey over represents species
1. This is likely due to the biases in
commercial sampling, with the fisheries not targeting the areas where species 1
are present, and the biases in the survey sampling from over representation of
the spatial distribution.

>>>>

To answer these questions we i) develop a simulation model where population
dynamics are highly-resolved in space and time by use of a Gaussian spatial
process to define suitable habitat\replaced[id=PD]{. Precise locations being}{
	and are} known \added[id=PD]{directly} rather than inferred from
sampling or commercial catch\added[id=PD]{, we can use the population model to
	validate how inference from fisheries-dependent and fisheries
	independent sampling relates to the real community structure in a way
	we could not with real data}. We ii) compare, at different spatial and
temporal aggregations, the 'real population' distributions to samples from
fisheries-dependent and fisheries independent catches to test if these are a
true reflection of the relative density of the populations. We then iii)
simulate a fishery closure to protect a species based on different spatial and
temporal data aggregations. We use these evaluations to draw inference on the
utility of commercial data in supporting management decisions.
\todo{\added[id=JJ]{If the paper has two goals this should be clear from the
		start, but may be better over 2 MSs}\added[id=PD]{I would like
		to keep both parts, but have made clearer in how its set out.
		The closure scenarios form validation of the data aggregation,
		rather than effectiveness of the closures themselves - so its a
		continuation of the same question in my eyes}}\deleted[id=PD]{.
	Further, we extend our analysis to a range of spatial and temporal
	scales to assess the impact of these processes on the success of the
	management measure.}\\

@@

\deleted[id=PD]{The fishing model operated on a tow-by-tow basis, while}
\replaced[id=PD]{P}{p}opulation dynamics (fishing and natural mortality which
are instantaneous rates, growth of the population biomass) operate on a daily
time-step\replaced[id=PD]{, while p}{. P}opulation movement occurs on a weekly
time-step\replaced[id=PD]{. R}{, while r}ecruitment \replaced[id=PD]{takes
	place}{occurs} periodically each year for a set time
\replaced[id=PD]{duration}{period (e.g. 3 weeks)} specified for each
population\deleted[id=PD]{.}\added[id=PD]{, while the fishing module operates
	on a tow-by-tow basis (i.e. multiple events a day)}.
\deleted[id=PD]{Here we describe each of the model components; 1) Population
	dynamics, 2) Recruitment dynamics, 3) Population movement dynamics, 4)
	fishery dynamics.}

Population movement is a combination of random (diffusive) movement, governed
by a stochastic process where movement between adjacent cells is described by a
set of probabilities, and directed (advective) movement where at certain times
of year the population moves towards spawning grounds by increasing the
probabilities of moving into the spawning grounds from adjacent cells. We
incorporate characterisation of a number of different fishing
\added[id=PD]{fleet dynamics} exploiting four fish populations with different
spatial and population demographics. The following describes the implementation
of each of the sub-modules.

@@

The basic population level processes were simulated using a modified two-stage
Deriso-Schnute delay difference model which models the fish populations in
terms of aggregate biomass of recruits and mature components rather than
keeping track of individuals\citep{Deriso1980, Schnute1985, Dichmont2003}.
\added[id=PD]{A daily time-step was chosen to discretise continuous population
	processes on a biologically relevant and computationally tractable
	timescale.} \deleted[id=PD]{Here,}Population biomass growth and
depletion for pre-recruits and\deleted[id=PD]{fish} recruited
\added[id=PD]{fish}\deleted[id=PD]{to the fishery} were modelled separately as
a function of previous recruited biomass, intrinsic population growth and
recruitment functionally linked to the adult population size.  Biomass for each
cell $c$ was incremented each day $d$ as follows (the full parameter list is
detailed in Table \ref{tab: pop_variable}): 
\begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& (1 + \rho) B_{c,d} \cdot e^{-Z_{c,d}} - \rho \cdot e^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& (B_{c,d-1} \cdot e^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
	R_{\tilde{y}(c,y,d-1)})
	\hspace{0.4cm} + \\
	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(c,y,d)} 
	\end{split}
\end{equation}
where $\rho$ is Brody's coefficient, shown to be equal to $e^{-K}$ when $K$ is
the growth rate from a von Bertalanffy logistic growth model
\citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
represents the proportion of fish recruited during that day for the year, while
$R_{c,\tilde{y}}$ is the annual recruits in cell $c$ for year $y$. \\

@@

A fisheries-independent survey is simulated where fishing on a regular grid
begins each year at the same time for a given number of stations (a fixed
station survey design). Catches of the populations \replaced[id=JJ]{at each
	station}{present} are recorded but not removed from the population
(catches are assumed to have negligible impact on population dynamics). This
provides a fishery independent snapshot of the populations at a regular spatial
\replaced[id=JJ]{intervals}{distribution} each year, similar to scientific
surveys undertaken by fisheries research agencies. \\

@@

The following steps are undertaken to determine closures:
\todo{\added[id=JJ]{Procedure unclear. Refer to symbols in methods section or
		switch order starting with description of data type
		etc..}\added[id=PD]{Yes, will redo}}
\begin{enumerate}
	\item Extract data source
	\item Aggregate according to desired spatial and temporal resolution
	\item Interpolate across entire area at desired resolution using simple
		bivariate kriging using the \emph{interp} function from the R
		package akima \citep{Akima2006}. This is intended to represent
		a naive spatial model of catch rates, without knowledge of the
		spatial population dynamics.
	\item Close area covering top 5 \% of catch rates 
\end{enumerate}
In total 28 closure scenarios were run that represent combinations of:

@@

Vessels from the same fleet (and therefore targeting preference) may exploit
some shared and some different fishing grounds depending on their own personal
experience during the explore phase of the fishery (\added[id=PD]{Figure}
\ref{S-fig:14}). This results from the randomness in the correlated random walk
step function, with distance moved during the exploitation phase and the
direction stochastically related to the revenue experienced on the fishing
ground (\replaced[id=PD]{Figure}{while}
\ref{S-fig:15}).\todo{\added[id=JJ]{Move some of the supplementary figures to
		the manuscript}}

@@

Figure \ref{fig:2} shows the consequences of different temporal aggregations of
the data over a ten-year period, with weekly (top), monthly (middle) and yearly
(bottom) catch compositions from across an aggregated 20 x 20 area. By
comparison to the 'real population', the monthly aggregation captures the major
patterns seen in the weekly data, albeit missing more subtle differences. The
yearly data assumes the same proportion of each population caught at any time
of the year due to the data aggregation. This assumption introduces
`aggregation bias' as the data may only be representative of some point (or no
point) in time. The commercial data on a weekly basis shows some of the same
patterns as the 'real population', though the first species (in red) is less
well represented and some weeks are missing catches from the area. The monthly
data shows some consistency between the 'real population' and commercial data
for species 2 - 4, though species 1 remains under-represented. On an annual
basis, interestingly the commercial data under represents the first species (in
red) while the survey over represents species
1. This is likely due to the biases in commercial sampling, with the fisheries
not targeting the areas where species 1 are present, and the biases in the
survey sampling from over representation of
the spatial distribution.
